A Parallel General Purpose Multi-Objective Optimization Framework, with Application To Electron Beam Dynamics

### 2019-02-01 paper/submission/prab.tex
Removed code listing 1 and 4

%
The \textsc{Pilot} component acts as a bridge between the optimizer and
  forward solvers, providing the necessary functionality to handle passing
  requests and results between the \textsc{Optimizer} and the
  \textsc{Simulation} modules.
The framework was implemented in \texttt{C++}, utilizing features like template
  parameters to specify the composition of the framework (shown in Listing 1).

%\noindent\begin{minipage}{0.48\textwidth}
%\noindent
\begin{code}[Assembling the optimizer \\ from components]
typedef InputFileParser	Input_t;
typedef PisaVariator	Opt_t;
typedef OpalSimulation	Sim_t;

typedef Pilot< Input_t, Opt_t, Sim_t > Pilot_t;
\end{code}
%\end{minipage}
The framework provides ``default'' implementations that can be controlled via
  command line options.
Due to its modular design, all components can be completely customized.

@@

To improve the expressive power of objectives and constraints, a
  simple mechanism to define and call custom functions in expressions was introduced.
Using simple functors, e.g. as the one shown in Listing 4, to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
  booleans, strings or floating point values.

\begin{code}[Simple Average Functor]
struct avg {

    double operator()(
      client::function::arguments_t args) const {

        double limit = boost::get<double>(args[0]);
        std::string filename =
          boost::get<std::string>(args[1]);

        double sum = 0.0;
        for(int i = 0; i < limit; i++)
            sum += getDataFromFile(filename, i);

        return sum / limit;
    }
};
\end{code}

@@

In contrast to approaches that are tightly coupled to the optimization
  algorithm, the range of possible applications is much wider.
Even in cases where the mathematical model of the forward solver is not known
  exactly, fixed or on the real time measurements can be used to guide the
  search for the Pareto optimal solutions.
Finally, combining the presented multi-objective optimization framework with
  a physicist long standing experience in the field provides a solid basis
  for better understanding and improving the decision making process in the
  design and operation of particle accelerators.

>>>>

%
The \textsc{Pilot} component acts as a bridge between the optimizer and
  forward solvers, providing the necessary functionality to handle passing
  requests and results between the \textsc{Optimizer} and the
  \textsc{Simulation} modules.
The framework was implemented in \texttt{C++}, utilizing features like template
parameters to specify the composition of the framework.
``Default'' implementations are provided that can be controlled via command line options.
Due to its modular design, all components can be completely customized.

@@

To improve the expressive power of objectives and constraints, a
  simple mechanism to define and call custom functions in expressions was introduced.
Using simple functors, to compute an
  average over a set of data points, enriches expressions with custom
  functions.
Custom function implementations overload the \texttt{()} parenthesis operator.
The function arguments specified in the corresponding expression are stored in
  a \texttt{std::vector} of Boost variants~\cite{boost2} that can be
  booleans, strings or floating point values.

@@

In contrast to approaches that are tightly coupled to the optimization
algorithm, the range of possible applications is much wider.
Even in cases where the mathematical model of the forward solver is not known
exactly, fixed or on the real time measurements can be used to guide the
search for the Pareto optimal solutions.
Finally, combining a multi-objective optimization framework such as 
the one presented with practical experience in the field should expedite 
the decision making process in the design and operation of particle 
accelerators.
